% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

\documentclass[a4paper,11pt]{article} 
\usepackage[T1]{fontenc}
\usepackage{lmodern,mathptmx}
\usepackage[margin=2cm]{geometry}
\usepackage[parfill]{parskip}
\usepackage[colorlinks,linkcolor = black,urlcolor = black]{hyperref}

\title{New Member Application}
\author{UK \TeX\ Users Group}
\date{2009}

\newcommand{\ShowBoxed}[1]{%
  \fbox{%
    \begin{minipage}{\textwidth}
      \raggedright
	  \smallskip
	  #1
	  \medskip
	\end{minipage}
  }%
  \hspace*{-10bp}%
}	
	
\begin{document}
\thispagestyle{empty}

\begin{minipage}{\textwidth}
  \makeatletter
  {\Large \@author}
  
  \smallskip
  
  {\large \@title\ \@date}
  
  \medskip
\end{minipage}

The information you supply will be held in a database and used
for the purposes of managing your UK-TUG membership and the 
affairs of the society. (The Constitution, available at
\url{http://uk-tug-archive.tug.org/Constitution/}, defines these).

If you apply for joint TUG and UK-TUG membership, you agree to 
TUG's data protection policy, (see 
\url{http://tug.org/join.html#privacy}) and to UK-TUG passing 
on your details to TUG. TUG stores and processes your details 
outside Europe.

New members will be sent a free copy of the current DVD ``\TeX\ 
Live 2008''. This allows easy installation of \TeX\ and friends, 
including \LaTeX, on different operating systems for example 
Windows XP, Windows Vista, MacOS X and GNU-Linux.  

Please tick one membership option, complete and send this form 
with your cheque (including any optional donation) to:

\begin{minipage}{\textwidth}
  \bfseries
  Joseph Wright\\
  UK-TUG Membership Secretary\\
  2, Dowthorpe End\\
  Earls Barton\\
  Northamptonshire\\
  NN6~0NH
\end{minipage}

\medskip

\begin{itemize}
  \item [[~]] Membership of UK-TUG at \pounds10.
  \item [[~]] Joint TUG and UK-TUG membership at \pounds47.
  \item [[~]] Joint TUG and UK-TUG membership at the 
    concessionary\textsuperscript{*} \pounds30.
\end{itemize} 
Joint members do not receive duplicate printed material or
software from TUG where UK-TUG already supplies it. This saving
allows the additional fee for joint membership to be less than the
standard TUG membership fee.

\textsuperscript{*}~Concessions: full time student, state pension. 
Please send relevant photocopy with your application.

\ShowBoxed{%
  I enclose a cheque for \pounds \hspace{1cm} made payable to 
  UK \TeX\ Users Group (or UK-TUG), including an optional 
  donation of  \pounds \hspace{1cm} to UK-TUG and an optional 
  donation of \pounds  \hspace{1cm} to the \LaTeX3 fund. 

  \medskip

  \textbf{Signed: \hspace{6cm} Date:}
}

\ShowBoxed{%
  \bfseries
  Name: \\
  Postal address: \\[1cm]
  E-mail address:
}

\ShowBoxed{%
  \textbf{UK-TUG Membership Directory: (optional)} \\
  
  If you wish to be entered in or receive the UK-TUG Membership
  Directory, you must tick an option and \emph{sign below}.
  \begin{itemize}
    \item[[~]] I would like a copy of the UK-TUG Membership 
      Directory.
    \item[[~]] I would like to appear in the UK-TUG Membership
      Directory.
  \end{itemize}

  I agree that my name and email details may be supplied to 
  other members only and I also agree that if members details
  are supplied to me, I will not distribute them further or use 
  them inappropriately.
  
  \medskip

  \textbf{Signed: \hspace{6cm} Date:}
}

\end{document}
