\documentclass[a4paper,11pt,UKenglish]{article}

\usepackage{babel}

\usepackage{lmodern}
\usepackage[T1]{fontenc} 

\usepackage[parfill]{parskip}
\usepackage{geometry}
\geometry{margin = 2cm}

\usepackage{hyperref}
\hypersetup{hidelinks}

\title{Membership Form}
\author{UK \TeX{} Users Group}
\date{2016}

\newcommand{\ShowBoxed}[1]{%
  \fbox{%
    \begin{minipage}{\textwidth}
      \raggedright
	  \smallskip
	  #1%
	  \medskip
	\end{minipage}
  }%
  \hspace*{-10 bp}%
}	
	
\begin{document}
\thispagestyle{empty}

\begin{minipage}{\textwidth}
  \makeatletter
  {\Large \@author}
  
  \smallskip
  
  {\large \@title{} \@date}
  
  \medskip
\end{minipage}

The information you supply will be held in a database and used for the purposes
of managing your UK-TUG membership and the affairs of the group (as detailed in
the Constitution, see \url{http://uk-tug-archive.tug.org/about/constitution/}).

If you apply for joint TUG and UK-TUG membership, you agree to TUG's data
protection policy, (see \url{http://tug.org/join.html#privacy}) and to UK-TUG
passing on your details to TUG. TUG stores and processes your details outside
Europe.

Members will be sent a free copy of the current \TeX{} Collection DVD. This
allows easy installation of \TeX{} and friends, including \LaTeX{}, on Windows,
MacOS X and GNU-Linux.

Please tick one membership option, complete and send this form with your cheque
to the address below.

\begin{minipage}{\textwidth}
  \bfseries
  Joseph Wright\\
  UK-TUG Membership Secretary\\
  2, Dowthorpe End\\
  Earls Barton\\
  Northamptonshire\\
  NN6~0NH
\end{minipage}

\medskip

\begin{itemize}
  \item [[~]] Membership of UK-TUG at \pounds 10.
  \item [[~]] Joint TUG and UK-TUG membership at \pounds 50.
  \item [[~]] Joint TUG and UK-TUG membership at the 
    concessionary\textsuperscript{*} \pounds 35.
\end{itemize}
\textsuperscript{*}~Concessions: full-time student, state pension. Please send
relevant photocopy with your application \emph{if not seen previously by
UK-TUG}.

\begin{itemize}
  \item [[~]] \emph{Optional:} Please do not supply any printed materials
    (including \emph{TUGboat} for joint TUG members).
\end{itemize}

\ShowBoxed{%
  \bfseries
  Name: \\[0.2 cm]
  E-mail address:\\[0.2 cm]
  Postal address: \\[1.5 cm]
}

\ShowBoxed{%
  \textbf{Payment details}
  \begin{itemize}
    \item Membership fees \pounds
    \item \emph{Optional} donation to UK-TUG \pounds
    \item \emph{Optional} donation to \LaTeX3 Fund \pounds\\[0.25 em]
  \end{itemize}
  Please make cheques payable to  `UK TeX Users Group' or `UK-TUG'.\\[0.25 em]
}

\ShowBoxed{%
  \textbf{\emph{Optional}: UK-TUG Membership Directory}\\[0.25 cm]
  
  I wish to appear in the UK-TUG Membership Directory. I understand that my
  name and e-mail address will be supplied to other members of UK-TUG.
  
  \bigskip

  \textbf{Signed: \hspace{6cm} Date:}
}

\end{document}
